\chapter{The Frontend}
\label{frontend}
\subsection{Technology Stack}
In the construction of our system, we will need a number of open source technologies, libraries and standards to support our
develepoment. An exhaustive list is given below
\begin{itemize}
	\item HTML5
	\item CSS3
	\item Javascript
	\item React.Js
	\item Boostrap
\end{itemize}
\subsubsection{HTML5}
HTML5 is a markup language mainly used for structuring content on 
the World Wide Web. The its last major version(version 5.0) it is recommended
by the World Wide Web Consortium (W3C). The responsible organisation WHATWG 
(Web Hypertext Application Technology Working Group) is a consortium of the 
major browser vendors(Apple, Google, Mozilla, and Microsoft)\cite{gudeliauskas_2019}.
\subsubsection{CSS3}
CSS stands for Cascading Style Sheets with an emphasis placed on “Style.” 
While HTML is used to structure a web document, CSS comes through and 
specifies your document’s style—page layouts, colors, and fonts are all 
determined with CSS\cite{morris_2020}. We will use CSS, version 3, to make our frontend
application aesthecaly pleasing and easy-to-use for our end-users.
\subsubsection{Javascript}
longside HTML and CSS, JavaScript is one of the major technologies of the World Wide Web.
JavaScript makes possible interactive web pages and is an integral part of web applications. 
\subsubsection{React}
React (also known as React.js or ReactJS) is an open-source, front end, JavaScript library[3] for 
building user interfaces or UI components. It is maintained by Facebook and a community of individual developers and companies.[4][5][6] 
React can be used as a base in the development of single-page or mobile applications. However, React is only concerned with state 
management and rendering that state to the DOM, so creating React applications usually requires the use of additional libraries for 
routing.[7][8] React Router[9] is an example of such a library. 
\subsubsection{Boostrap}
Bootstrap is a free and open-source CSS framework directed at responsive, mobile-first front-end web development. 
It contains CSS- and (optionally) JavaScript-based design templates for typography, forms, buttons, navigation, and 
other interface components.Bootstrap is among the most starred projects on GitHub, with more than 142,000 stars, behind 
freeCodeCamp (almost 312,000 stars) and marginally behind Vue.js framework.[2] 
